Gravitational Lens Modeling in a Citizen Science Context

### 2014-07-31 text/ms.tex
Added screenshot. Fixes #17

One begins by going to the \spl \phil{web application\footnote{\bf Phil
asks: should we provide a spl url here?}} and entering the number of a
\sw image tile.  \spl then presents the image, along with zoom and pan
options and a markup tool to construct a spaghetti diagram.  The human
modeller now has to make an educated guess for the topography of the
arrival-time surface, and input the locations time-ordering of the
maxima, minima, and saddle-points.  The markup tool \citep[which is
inspired by Figure~6 of][and is like that figure made interactive and
overlaid on data]{1986ApJ...310..568B} lets the modeller enter the
information by sketching saddle-point contours.  Examples can be seen
in the upper-left panels of Figures \ref{fig:6941} to \ref{fig:7022}. 
The loops in the markup tool were the origin of the ``spaghetti''
metaphor.

>>>>

One begins by going to the \spl \phil{web application\footnote{\bf
Phil asks: should we provide a spl url here?}} and entering the number
of a \sw image tile.  \spl then presents the image, along with zoom
and pan options and a markup tool to construct a spaghetti diagram. 
The human modeller now has to make an educated guess for the
topography of the arrival-time surface, and input the locations
time-ordering of the maxima, minima, and saddle-points.  The markup
tool \citep[which is inspired by Figure~6 of][and is like that figure
made interactive and overlaid on data]{1986ApJ...310..568B} lets the
modeller enter the information by sketching saddle-point contours. 
Examples can be seen in Figure~\ref{fig:screenshot} and the upper-left
panels of Figures \ref{fig:6941} to \ref{fig:7022}.  The loops in the
markup tool were the origin of the ``spaghetti'' metaphor.

\begin{figure}
  \centering
    \includegraphics[width=0.90\linewidth]{fig/screenshot}
  \caption{\phil{Screen grab of \spl in action. A \sw image has been loaded
  in, re-centred and zoomed, and 5 images and associated time delay
  surface `spaghetti'' contours suggested, using the marking tools
  associated with the buttons along the top of the panel. The mass
  model is optimized server-side 
  when the right-most button is pressed.}}
  \label{fig:screenshot}
\end{figure}
